---
title: "@ellessenne {xaringan} theme"
author: "Alessandro Gasparini"
date: "Last updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "ellessenne.css", "ellessenne-fonts.css"]
    nature:
      titleSlideClass: [bottom, left, inverse]
      highlightStyle: solarized-light
      ratio: "16:10"
      countIncrementalSlides: false
---

```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
knitr::opts_chunk$set(fig.retina = 2, fig.align = "center", fig.height = 4, fig.width = 6)
```

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
remotes::install_github("yihui/xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader".

.footnote[
[1] 中文用户请看[这份教程](https://slides.yihui.org/xaringan/zh-CN.html)

[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
]

---

# Extra colours

The theme includes extra colours and font sizes.

Colours: .grey[`.grey[]`], .white[`.white[]`], .black[`.black[]`], .main[`.main[]`], .accent[`.accent[]`], .text[`.text[]`], .text-inverse[`.text-inverse[]`].

The colours of the theme can be easily customised - see `ellessenne.css`.

---

# Extra font sizes:

The theme includes extra colours and font sizes.

Font-sizes: .tiny[(.)tiny[]], .scriptsize[(.)scriptsize[]], .footnotesize[(.)footnotesize[]], .small[(.)small[]], .normalsize[(.)normalsize[]], .large[(.)large[]], .Large[(.)Large[]], .LARGE[(.)LARGE[]], .huge[(.)huge[]], .Huge[(.)Huge[]], .references[(.)references[]].

---

# Lists

1. One

2. Two

3. Three


* A

* B

* C

---

# R output

```{r cars}
s <- summary(cars)
s
```

---

# Plot

```{r pressure, echo = FALSE}
plot(pressure)
```
